Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis

### 2015-12-13 paper/EEST/First_Submission/Biographies/EEST-D-15-00056_biographies.tex

\textbf{Simon Bonner} is an Assistant Professor jointly appointed between the Department of Statistical and Actuarial Sciences and the Department of Biology at the University of Western Ontario, London, Ontario, Canada (sbonner6@uwo.ca). His research focuses primarily on developing statistical methods for the analysis of ecological data with particular emphasis on Bayesian methods for analyzing data from mark-recapture studies of wild animals. This work was completed while Simon was an Assistant Professor in the Department of Statistics at the University of Kentucky.

>>>>

\textbf{Edward Roualdes} is a swell guy who is more than capable of writing his own bio.

\textbf{Simon Bonner} is an Assistant Professor of Environmetrics jointly appointed between the Department of Statistical and Actuarial Sciences and the Department of Biology at the University of Western Ontario, London, Ontario, Canada (sbonner6@uwo.ca). His research focuses primarily on developing statistical methods for the analysis of ecological data with particular emphasis on Bayesian methods for analyzing data from mark-recapture studies of wild animals. This work was completed while Simon was an Assistant Professor in the Department of Statistics at the University of Kentucky.

\textbf{Thomas Whitney} is a PhD student in the Warnell School of Forestry and Natural Resources at the University of Georgia, Athens, GA (thomas.whitney@uga.edu).  He is broadly interested in community ecology and uses molecular tools to characterize interactions between predators and prey, parasites and hosts, and herbivores and primary producers.
